### 2023-12-31 docs/projects/data-formats/hdf/index.qmd
rerendered HDF tutorial under the new position

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scicloj.scrapbook.hdf.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scicloj.scrapbook.hdf_files/md-default3.js" type="text/javascript"></script><script src="scicloj.scrapbook.hdf_files/md-default4.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

@@

<div class="sourceClojure">
```clojure
(ns scicloj.scrapbook.hdf
  (:require [babashka.fs :as fs]
            [tech.v3.tensor :as tensor]
            [clojure.java.io :as io]
            [clojure.string :as string]
            [scicloj.noj.v1.vis.image :as vis.image]
            [tech.v3.datatype.functional :as fun])
  (:import io.jhdf.HdfFile
           java.io.File))
```
</div>

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">{:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[112 110 111 ... 114 118 124]
 [105 112 106 ... 115 120 119]
 [107 109 108 ... 117 123 115]
 ...
 [132 138 134 ... 109 107 109]
 [130 129 129 ... 115 111 103]
 [134 135 134 ... 110 111 110]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[124 120 121 ... 117 121 124]
 [118 123 117 ... 118 122 121]
 [120 123 117 ... 119 123 118]
 ...
 [133 139 136 ... 111 106 108]
 [133 132 131 ... 116 111 103]
 [136 137 135 ... 114 111 108]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[125 120 120 ... 116 121 127]
 [116 122 116 ... 117 121 119]
 [120 121 115 ... 120 123 118]
 ...
 [132 139 133 ... 112 107 108]
 [135 132 132 ... 115 112 104]
 [134 135 135 ... 114 112 108]]}
</code></pre></div><img src="scicloj.scrapbook.hdf_files/2.png" style="width:100%;" /></div><p>)</p></div>

@@

<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-sources/hdf/notebooks/scicloj/scrapbook/hdf.clj</small></small></pre></div>

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default3.js" type="text/javascript"></script><script src="index_files/md-default4.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

@@

<div class="sourceClojure">
```clojure
(ns index
  (:require [babashka.fs :as fs]
            [tech.v3.tensor :as tensor]
            [clojure.java.io :as io]
            [clojure.string :as string]
            [scicloj.noj.v1.vis.image :as vis.image]
            [tech.v3.datatype.functional :as fun])
  (:import io.jhdf.HdfFile
           java.io.File))
```
</div>

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">{:key "0", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[112 110 111 ... 114 118 124]
 [105 112 106 ... 115 120 119]
 [107 109 108 ... 117 123 115]
 ...
 [132 138 134 ... 109 107 109]
 [130 129 129 ... 115 111 103]
 [134 135 134 ... 110 111 110]]}
</code></pre></div><img src="index_files/0.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "1", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[124 120 121 ... 117 121 124]
 [118 123 117 ... 118 122 121]
 [120 123 117 ... 119 123 118]
 ...
 [133 139 136 ... 111 106 108]
 [133 132 131 ... 116 111 103]
 [136 137 135 ... 114 111 108]]}
</code></pre></div><img src="index_files/1.png" style="width:100%;" /><div><pre><code class="language-clojure">{:key "10", :data #tech.v3.tensor&lt;int32&gt;[600 800]
[[125 120 120 ... 116 121 127]
 [116 122 116 ... 117 121 119]
 [120 121 115 ... 120 123 118]
 ...
 [132 139 133 ... 112 107 108]
 [135 132 132 ... 115 112 104]
 [134 135 135 ... 114 112 108]]}
</code></pre></div><img src="index_files/2.png" style="width:100%;" /></div><p>)</p></div>

@@

<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>
